\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States

### 2018-07-23 paper/manuscript.tex
finished revising the boilerplate section

% BRUCE HERE
\begin{itemize}
\item The length of the line and the number of tokens are a way to find lines consisting of only a word or two. This is highly predictive of lines which are used as website headers and navigational elements, which are of of zero substantive interest to us. These terms also happen to be fairly common, which causes them to be overweighted by the topic model.

\item To directly address the latter problem, a measure for the number of times a line is duplicated within a city is included. Many lines occur hundreds or even thousands of times on a single website, and therefore are terms that are highly predictive of the website, which causes the topic model to create topics that are highly correlated with cities.

\item Finally, the distance measure: Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths). Since lines can occur in multiple documents, or multiple times in the same document, we take the median of these measures. Thus, for example, a line which often occurs at the beginning of documents might have a score of 0.45, whereas a line that tends to be found more in the center, and thus be indicative of more relevant content, might be scored with a 0.11 instead.
\end{itemize}

We rely on random forests as a classifier, which offer slightly better performance than logit\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} and have the added benefit of giving estimates of variable importance. Performance of this classifier was assessed through five-fold cross-validation, the results of which can be found in table \ref{randomForest}.

@@

This classifier is then used to flag and remove all lines that are not classified as substantively useful. The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e. a city that isn't part of our sample used in the analysis) as an example in Figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4}. Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common. After the removal, the distribution looks more like what it should be - lines of medium length now occur more frequently than extremely short ones (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}). Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}). Finally, the position of the line within the documents is not as important to the random forest, and this also shows in the results. However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}). After all the preprocessing is set and done, our corpus consists of 259,099 documents.

>>>>

% BRUCE HERE
\begin{itemize}
\item {\bf Line length:} The length of the line and the number of tokens are ways to find lines consisting of only a word or two. This is highly predictive of lines which are used as website headers and navigational elements, which are of of zero substantive interest to us, but are very effective at differentiating cities. These terms also happen to be fairly common, which causes them to be overweighted by the topic model.

\item {\bf Number of line duplications:} To directly address the latter problem, we include a measure of the number of times a line is duplicated within a city. Many lines occur hundreds or even thousands of times on a single website, and therefore are terms that are highly predictive of the website, which causes the topic model to find topics that are highly predictive of cities, but not substantively informative.

\item {\bf Line position in the document} Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths). Since lines can occur in multiple documents, or multiple times in the same document, we take the median of these measures. Thus, for example, a line which often occurs at the beginning of documents might have a score of 0.45, whereas a line that tends to be found more in the center, and thus be indicative of more relevant content, might be scored with a 0.11 instead.
\end{itemize}

@@

We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assessed performance of this classifier through five-fold cross-validation [@markus, please add another sentence describing the five-fold CV], the results of which can be found in Table \ref{randomForest} [@markus, what package was used for this RF?]. [@markus, check that your writing is consistent with first-person plural] We use this classifier to flag and remove all lines that are not classified as substantively meaningful [@markus, how is the RF used to flag boilerplate lines (e.g., using a threshold of p = 0.5?]. The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e. a city that isn't part of our sample used in the analysis) as an example in Figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4}. Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common. After the removal, the distribution looks more like what it should be [@markus, why is this what it "should be"]---lines of medium length now occur more frequently than extremely short ones (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}). Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}). Finally, the position of the line within the documents is not as important to the random forest, and this also shows in the results. However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}). [@markus, this is an excellent demonstration of the effect of the classifier. When you get a chance, would you also add a table listing the top 10 most likely boilerplate lines---to provide face validity that we are accurately flagging boilerplate?] After all the preprocessing is set and done, our corpus consists of 259,099 documents.
